\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyperref}
\input{glyphtounicode}


% ----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 


\begin{document}

\begin{center}
  \textbf{\Huge \scshape Sikander Nawaz} \\ \vspace{1pt}
  \textbf{\small \scshape Software Engineer and Tech Trainer} \\ \vspace{5pt}
  \small +92 313 4140481 $|$
  \href{mailto:sikandernawaz295@gmail.com}{sikandernawaz295@gmail.com}  $|$
  \href{https://www.linkedin.com/in/sikander-nawaz/}{\underline{LinkedIn}} $|$
  \href{https://github.com/sikander-nawaz}{\underline{GitHub}} $|$
  \href{https://leetcode.com/u/sikander_09/}{\underline{LeetCode}}
\end{center}

%-----------1 - ACHIEVEMENTS-----------
\section{\textbf{Achievements}}
\resumeItemListStart
\resumeItem{\textcolor{blue}{\itshape @Harvard University(CS50x\_PuzzleDay\_Winner):} Our team {\href{https://www.linkedin.com/feed/update/urn:li:activity:7184638208993873920/}{\underline{won 1st place}}} at CS50x Puzzle Day 2024 by solving 9/9 complex puzzles.}
\resumeItem{\textcolor{blue}{\itshape @Stanford University(Code\_in\_Place):} {\href{https://www.linkedin.com/feed/update/urn:li:activity:7223990886295064576/}{\underline{Selected}}} as a Section Leader to teach Python to international students.}
\resumeItem{\textcolor{blue}{\itshape @iCodeGuru:} Offers volunteer teaching in {\href{https://github.com/sikander-nawaz/Python_Volunteer_Teaching}{\underline{Python}}}, {\href{https://github.com/sikander-nawaz/DSA_Volunteer_Teaching}{\underline{DSA}}} and {\href{https://www.youtube.com/watch?v=b366KTKppyU&list=PLe-jr3hh4N_mE6iQg-GiaCpu4cBEn6LVq&index=1}{\underline{Duolingo}}}.}
\resumeItem{\textcolor{blue}{\itshape @Beaconhouse National University:} Conduct a {\href{https://www.linkedin.com/posts/sikander-nawaz_metaabrhackerabrcupabr2024-activity-7240238291101347842-o2Lq?utm_source=share&utm_medium=member_desktop}{\underline{webinar}}} to spread awareness about Meta Hacker Cup in Pakistan. }
\resumeItem{\textcolor{blue}{\itshape @lablab.ai:} {\href{https://lablab.ai/u/@sikander_09}{\underline{Participated}}} in multiple AI International Hackathons.}
\resumeItem{\textcolor{blue}{\itshape @SMIT:} Completed {\href{https://www.linkedin.com/posts/sikander-nawaz_anas-anas-smit-activity-7140334845901131777-kpEH?utm_source=share&utm_medium=member_desktop}{\underline{MERN Stack}}} from Saylani Mass IT Training Program Faisalabad.}
\resumeItem{\textcolor{blue}{\itshape @leetcode:} {\href{https://leetcode.com/u/sikander_09/}{\underline{Solved}}} Data Structures and Algorithms problems.}



\resumeItemListEnd

%-----------2 - Technical SKILLS-----------
\section{\textbf{Technical Skills}}
\resumeItemListStart
\resumeItem{\textcolor{blue}{\itshape \textcolor{blue}{\itshape Programming Languages:}}{ C, C++, Python, JavaScript (ES6+) } \\}
\resumeItem{\textcolor{blue}{\itshape Web Dev:}{ HTML5, CSS3, SCSS, SASS, Bootstrap 5, Tailwind CSS, Shadcn UI, Chakra UI, Next JS, React JS(Context API, Router, State Management)} \\}
\resumeItem{\textcolor{blue}{\itshape Mobile Dev:}{ React Native} \\}
\resumeItem{\textcolor{blue}{\itshape Backend:}{ Firebase, Node JS, Express JS, Python} \\}
\resumeItem{\textcolor{blue}{\itshape Version Control:}{ Git, Github} \\}
\resumeItem{\textcolor{blue}{\itshape APIs:}{ Rest-APIs} \\}
\resumeItem{\textcolor{blue}{\itshape Databases:}{ MongoDB, Firestore}\\}
\resumeItemListEnd
%

%-----------3 - EDUCATION-----------
\section{\textbf{Education}}
\resumeSubHeadingListStart
\resumeSubheading
{Govt. Graduate College of Science Samanabad, Faisalabad}{Sep 2019 - Sep 2023}
{}{}
{CGPA: 3.39 / 4.00}{}
\resumeItemListStart
\resumeItem{Bachelor of Science in Computer Science}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------6 - VOLUNTEER Experience-----------
\section{\textbf{Volunteer Experience}}
\resumeSubHeadingListStart
\resumeSubheading
{Section Leader Mentor}{Apr 2024 -- Jun 2024}
{{\href{https://codeinplace.stanford.edu/}{\underline{Stanford University: Code in Place}}}}{California, United States · Remote}
\resumeItemListStart
\resumeItem{{\href{https://www.linkedin.com/feed/update/urn:li:activity:7223990886295064576/}{\underline{Selected as a Section Leader}}} for Stanford's Code in Place to teach Python to international students in groups of 10-15.}
\resumeItem{I also for one-on-one student support and taught TeachNow sessions.}
\resumeItem{ I helped 30+ international folks worldwide, including countries like the USA, Canada, Russia, the UK, India, Bangladesh, Brazil, Germany, and others.}
\resumeItemListEnd
\resumeSubheading
{Trainer and Moderator}{Feb 2024 -- Present}
{{\href{https://www.linkedin.com/company/icode-guru/mycompany/}{\underline{iCodeGuru}}}}{Santa Clara, California · Remote}
\resumeItemListStart
\resumeItem{{\href{https://github.com/sikander-nawaz/Python_Volunteer_Teaching}{\underline{Offered}}} volunteer teaching in Python at iCodeGuru, training to underprivileged students.}
\resumeItem{{\href{https://github.com/sikander-nawaz/DSA_Volunteer_Teaching}{\underline{Delivering}}} "Data Structures and Algorithms" from Scratch, emphasizing LeetCode.}
\resumeItem{{\href{https://www.youtube.com/watch?v=b366KTKppyU&list=PLe-jr3hh4N_mE6iQg-GiaCpu4cBEn6LVq&index=1}{\underline{Taught}}} course on the Duolingo English Proficiency Test.}
\resumeItem{{\href{https://github.com/Ahmadjajja/Machine-Learning_and_its-privacy-implications}{\underline{Moderate}}} "Machine Learning from Scratch \& Its Privacy Implications" course at iCodeGuru.}
\resumeItem{{\href{https://www.linkedin.com/posts/sikander-nawaz_announcement-icodeguru-is-excited-activity-7212688604307857408-Scw9?utm_source=share&utm_medium=member_desktop}{\underline{Moderate}}} "Strategies and Techniques to Excel the IELTS Exam" weekly workshop at iCodeGuru.}
%\resumeItem{See students' reviews about how I impacted their coding(DSA + LeetCode) journeys : ({\href{https://www.linkedin.com/posts/sikander-nawaz_dsa-dsa-leetcode-activity-7170805639886106624-Kxka?utm_source=share&utm_medium=member_desktop}{\underline{ Student1 }}}), ({\href{https://www.linkedin.com/posts/syedshahzilimran_mastering-trees-unlocking-the-key-of-dsa-activity-7174974045019398144-DN_C?utm_source=share&utm_medium=member_desktop}{\underline{ Student2 }}}), ({\href{https://www.linkedin.com/feed/update/urn:li:activity:7173635314391920640/}{\underline{ Student3 }}}) and many more. }%
\resumeItemListEnd
\resumeSubHeadingListEnd
%



%-----------7 - Hackathons & Competitions-----------
\section{\textbf{Hackathons and Competitions}}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{{Harvard's CS50x Puzzle Day 2024}} $|$ [{\href{https://www.linkedin.com/posts/sikander-nawaz_cs50xabrpuzzleabrdayabr2024-fullabrstackabrdeveloper-activity-7184638208993873920-m-y1?utm_source=share&utm_medium=member_desktop}{\underline{LinkedIn link}}}]}{}
\resumeItemListStart
\resumeItem{Led a 3-member team to 1st place at Harvard's CS50x Puzzle Day 2024.}
\resumeItem{Solved 9 complex puzzles using deep logical thinking and teamwork.}
\resumeItem{Collaborated with an international members from Bangladesh and Pakistan.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{{ResuMate}} $|$ \emph{HTML, CSS, Bootstrap5, Javascript, React, Open AI Model GPT-3.5 Llama 3, Pinecone, python, Flask} $|$ [{\href{https://github.com/sikander-nawaz/ResuMate}{\underline{Github link}}}]} {}
\resumeItemListStart
\resumeItem{AI-Powered Tool for Generating Personalized Job Application Responses and Cover Letters.}
\resumeItem{The Neue View Project involved a team of four individuals from United States, and Pakistan.The [{\href{https://lablab.ai/event/llama-3-ai-hackathon}{\underline{lablab.ai submission link}}}]}
\resumeItem{Junior Developer: Frontend Design (responsible for building the frontend and integrating APIs).}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{{NeuroFlow}} $|$ \emph{ HTML, CSS, Bootstrap5, Javascript, React, Gen AI, Machine Learning, python, Flask} $|$ [{\href{https://github.com/sikander-nawaz/NeuroFlow}{\underline{Github link}}}]}{}
\resumeItemListStart
\resumeItem{AI-Powered Image Classification and Specialist Assistant for Brain Tumor Diagnosis and Information.}
\resumeItem{The NeuroFlow Project involved a team of six individuals from Indoneshia, Bangladesh and Pakistan.The [{\href{https://lablab.ai/event/langflow-hackathon/ai-the-era/neuroflow}{\underline{lablab.ai submission link}}}]}
\resumeItem{Junior Developer: Frontend Design (responsible for building the frontend and collecting data to train model).}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{{Coding Competitions}}}{}
\resumeItemListStart
\resumeItem{Enrolled in Meta Hacker Cup 2024.}
\resumeItemListEnd
\resumeSubHeadingListEnd
%

%-----------8 - PERSONAL PROJECTS-----------
\section{\textbf{Personal Projects}}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{{Full Stack Bank WEB APP}} $|$ \emph{HTML, CSS, Bootstrap5, Javascript, React, Context API, Firebase, Firestore} $|$ [{\href{https://github.com/sikander-nawaz/Bank_App}{\underline{Github link}}}]}{}
\resumeItemListStart
\resumeItem{Authentication with email and password, as well as login via social media accounts like Google, Facebook, and Github.}
\resumeItem{The dashboard provides users with access to an ATM machine-like interface, where they can perform basic banking transactions such as withdrawing and depositing money.}
\resumeItem{Users can easily withdraw or deposit money from their accounts using the intuitive interface, which guides them through the process step-by-step.}
\resumeItem{The Bank-App also allows users to delete their account, in case they no longer wish to use the platform.}
\resumeItem{The application provides users with the ability to view all their existing accounts, providing a complete overview of their financial situation.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{{Tutor Finder}} $|$ \emph{HTML, CSS, Bootstrap, JavaScript, React JS, Express JS, Node JS, MongoDB} $|$ [{\href{https://github.com/sikander-nawaz/TutorFinder}{\underline{Github link}}}]}{}
\resumeItemListStart
\resumeItem{Integrated functionality for scheduling \textbf{online and onsite appointments} with selected tutors. }
\resumeItem{Implemented a responsive \textbf{user interface} for a seamless tutor discovery and booking experience. }
\resumeItem{Ensured \textbf{secure user authentication} and data management for both tutors and students. .}
\resumeItemListEnd



\end{document}